Dynamical Neural Network Models\\for Sequence Learning

### 2019-05-09 paper/main.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[draft]{graphicx}
\usepackage{amsmath}
\usepackage[backend=biber,sorting=none]{biblatex}
%\usepackage{geometry}
\usepackage{float}
\addbibresource{mybib.tex}

@@

In the above equations, $\sigma$ is the sigmoid activation function, $i_t$ is the input gate, $f_t$ is the forget gate, $g_t$ is the cell gate, $o_t$ is the output gate and the $c_t$ and $h_t$ are the cell and hidden states respectively. The $\ast$ operator is the element-wise product operator. The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units. \cite{jozefowicz2015empirical}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{../diagrams/lstm.png}
    \caption{The network architecture for the LSTM-online model. The LSTM cells maintain an internal hidden state.}
    \label{fig:lstm-online-model}
\end{figure}

@@

The network can be formulated as an equation in terms of the 250 length input vector $x_t$ and the ReLU non-linearity function $R(z)$:
\begin{equation}
    \text{TDNN}(x_t) = R\left(x_tW_{ih}^T + b_i\right)W_{ho}^T + b_h
    \label{eq:tdnn}
\end{equation}
The biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are initialized randomly uniformly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer. The weights are then learned through gradient descent.

@@

The change in the voltages of each of the neurons in the hidden layer $\frac{dV_h}{dt}$ at time $t$ can be written in terms of the input $x_t$, the scale for the connection between the input and hidden layer found through the data-based normalization $\lambda_{ih}$, the transferred connection and bias weights from the TDNN $\left(W_{ih}, b_{i}\right)$, and the neuron spike threshold $\tau$ as:

@@

Similarly the following equation models the change in the voltages of the neurons in the output layer of the TDSNN:

\begin{equation}
    \frac{dV^{\left(o\right)}_t}{dt} = \lambda_{ho} \left(W_{ho}^TS^{\left(h\right)}_{t} + b_h\right) - S^{\left(o\right)}_{t-1} \tau
\end{equation}

@@

\subsubsection*{Original Readout}
The original readout method proposed by Rueckauer et al. looks at the voltage of the output layer rather than the spikes. This readout method combined with the the subtractive reset mechanism of the spiking neurons in the conversion method perform well on various tasks, \cite{rueckauer2017conversion} but in some cases we may not want to use the voltages. One alternative may be to use the average sum of spikes over the total runtime $T$ in the output layer. This approximation of the TDNN output values can be written as:

@@

\subsubsection*{Negative Readout}
When the output values produced by the TDNN is negative, the average sum of spikes fails to account for the negative output values. To account for these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatenated. The same was done for the bias. The positive sum of spikes was subtracted from the negative sum of spikes and then divided by the runtime $T$ to obtain an approximation of the original network's output. For a TDNN that has $l$ neurons in the output layer, the change in voltage for each neuron $j$ in the output layer can be written as:

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\linewidth]{../results/conversion-loss.png}
    \caption{Average distance between the output of the TDNN and the TDSNN for different runtimes over the $20,000$ elements in the artificial dataset.}
    \label{fig:clfig}
\end{figure}

@@

While conversion is one way to train a neural network, it is a supervised method that is not energy efficient on hardware implementations. We propose a spiking neural network architecture, with $k$ inputs, each fully connected to $1$ of $k$ columns of $L$ Leaky Integrate-and-Fire (LIF) neurons with randomly initialized weights. \cite{gerstner2002spiking} Each neuron in each column has a zero-weight connection to each neuron in each of the other columns. The inter-column connections have a Hebbian-inspired update rule. To map the spikes from this network, we use the K-Nearest Neighbors model with the sum of spikes of each neuron in each column over the runtime $T$. \cite{beliaev2007time} The model diagram is shown in Figure \ref{fig:csnn-network-diagram}.

@@

\subsubsection*{Hebbian Learning Rule}
The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns. The weight change on spike in a connection from column $i$ to column $j$ is defined as follows:

\begin{equation}
    \Delta w_{ij} = \eta(s_{i} - \Tilde{s})(s_{j} -  \Tilde{s})
\end{equation}

where $\eta$ is the learning rate and $\Tilde{s}$ is the mean spiking activity in all the columns, defined as follows:

\begin{equation}
    \Tilde{s} = \frac{1}{k} \sum_{i = 1}^{k}{s_i}
    \label{eq:mean_spikes_equation}
\end{equation}

In equation \ref{eq:mean_spikes_equation}, $s_i$ is the sum of spikes in a column over the duration of the input. The weight updates for this model are computed at the end of each input rather than continuously.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[backend=biber,sorting=none]{biblatex}
%\usepackage{geometry}
\usepackage{float}
\addbibresource{mybib.tex}

@@

In the above equations, $\sigma$ is the sigmoid activation function, $i_t$ is the input gate, $f_t$ is the forget gate, $g_t$ is the cell gate, $o_t$ is the output gate and the $c_t$ and $h_t$ are the cell and hidden states respectively. The $\ast$ operator is the element-wise product operator. The biases $\left(b_i, b_f, b_g, b_o\right)$ and weights $\left(W_{ii}, W_{hi}, W_{if}, W_{hf}, W_{ig}, W_{hg},W_{io}, W_{ho}\right)$ are initialized uniformly randomly from $\left[-\frac{1}{\sqrt{k}}, \frac{1}{\sqrt{k}}\right]$, where $k$ is the number of hidden units. \cite{jozefowicz2015empirical}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{../diagrams/lstm.png}
    \caption{The network architecture for the LSTM-online model. The LSTM cells (teal) maintain an internal hidden state.}
    \label{fig:lstm-online-model}
\end{figure}

@@

The network can be formulated as an equation in terms of the 250 length input vector $x_t$ and the ReLU non-linearity function $R(z)$:
\begin{equation}
    \text{TDNN}(x_t) = R\left(x_tW_{ih}^T + b_i\right)W_{ho}^T + b_h
    \label{eq:tdnn}
\end{equation}
The biases $\left(b_i, b_h\right)$ and the weights $\left(W_{ih}, W_{ho}\right)$ are initialized uniformly randomly from $\left[-\frac{1}{\sqrt{k_i}}, \frac{1}{\sqrt{k_i}}\right]$, where $k_i$ is the number of input features to the respective layer. The weights are then learned through gradient descent.

@@

The change in the voltages of each of the neurons in the hidden layer at time $t$ can be written in terms of the input $x_t$, the scale for the connection between the input and hidden layer found through the data-based normalization $\lambda_{ih}$, the transferred connection and bias weights from the TDNN $\left(W_{ih}, b_{i}\right)$, and the neuron spike threshold $\tau$ as:

@@

Similarly, the following equation models the change in the voltages of the neurons in the output layer of the TDSNN:
\begin{equation}
    \frac{dV^{\left(o\right)}_t}{dt} = \lambda_{ho} \left(W_{ho}^TS^{\left(h\right)}_{t} + b_h\right) - S^{\left(o\right)}_{t-1} \tau
\end{equation}

@@

\subsubsection*{Original Readout}
The original readout method proposed by Rueckauer et al. looks at the voltage of the output layer rather than the spikes. This readout method combined with the the subtractive reset mechanism of the spiking neurons in the conversion method perform well on various tasks, \cite{rueckauer2017conversion} but in some cases we may not want to use the voltages. A more biologically inspired alternative for approximating the output could be the average sum of spikes over the total runtime $T$ in the output layer. This approximation of the TDNN output values can be written as:

@@

\subsubsection*{Negative Readout}
When the output values produced by the TDNN is negative, the average sum of spikes fails to account for the negative output values. To account for these negative spikes, the output layer was doubled in size and the negative weight matrix of the original connections was concatenated. The same was done for the bias. The positive sum of spikes was subtracted from the negative sum of spikes and then divided by the runtime $T$ to obtain an approximation of the original network's output.

For a TDNN that has $l$ neurons in the output layer, the change in voltage for each neuron $j$ in the output layer is changed to:

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{../results/conversion-loss.png}
    \caption{Average distance between the output of the TDNN and the TDSNN for different runtimes over the $20,000$ elements in the artificial dataset.}
    \label{fig:clfig}
\end{figure}

@@

While conversion is one way to train a spiking neural network, it is a supervised method that is still not energy efficient on hardware implementations. We propose a spiking neural network architecture, with $k$ inputs, each fully connected to $1$ of $k$ columns of $L$ Leaky Integrate-and-Fire (LIF) neurons with weights initialized uniformly randomly from $\left[0, 0.3\right]$. \cite{gerstner2002spiking} Each neuron in each column has a zero-weight connection to each neuron in each of the other columns. The inter-column connections have a Hebbian-inspired update rule. To map the spikes from this network, we use the K-Nearest Neighbors model with the sum of spikes of each neuron in each column over the runtime $T$. \cite{beliaev2007time} The model diagram is shown in Figure \ref{fig:csnn-network-diagram}.

@@

\subsubsection*{Hebbian Learning Rule}
The Hebbian learning rule for the CSNN model is defined in terms of the spiking activity of its $k$ columns over the runtime $T$. The sum of spikes in a column $c$ over the runtime is defined as:

\begin{equation}
    \gamma_c = \sum_{t = 1}^{T}{s_t^{\left(c\right)}}
\end{equation}

where $s_t^{\left(c\right)}$ is a binary vector that represents the spiking neurons at time $t$ in column $c$. The mean spiking activity for each neuron $\Tilde{s}$ is then defined as:

\begin{equation}
    \Tilde{s} = \frac{1}{k} \sum_{c = 1}^{k}{\gamma_c}
    \label{eq:mean_spikes_equation}
\end{equation}

The weight change on spike in connections from column $a$ to column $b$ for learning rate $\eta$ is defined as follows:

\begin{equation}
    \Delta w_{a,b} = \eta * (\gamma_a - \Tilde{s})\otimes(\gamma_b - \Tilde{s})
\end{equation}

The weight updates for this model are computed at the end of each input rather than continuously.
